### 2023-06-24 thesis/sections/3-exp-setup.tex
thesis

\cmtDK[inline]{15 pages}
\cmtDK[inline]{\\
    - what is ambiguity? \\
    - control over dataset \\
    - target object/target group/non-target group: \\
    ---- 1. how many objects? \\
    ---- 2. how many shared attributes? \\
    ---- 3. which shared attributes? \\
    ---- 4. level of ambiguity \\
    - as close to CLEVR as possible \\
    ---- image size \\
    ---- number (10.000) \\
    ---- between 3 to 10 objects ??? \\
    - unambigous dataset: \\
    ---- target group = non-target group \\
    ---- all attributes shared, except for the color \\
    ---- \ \  --> describable with one 'word'
}
In this section I will describe which experiments were conducted to answer the \cmtDK{?}{questions} from the previous sections as well as the setup of these experiments. This will be done in two parts. The first part contains the creation of the datasets that will be used in the experiments. In the second part I will go deeper into discussing each experiment, including the necessity of the experiment, the specifities of the dataset, as well as the final architecture of the models.

@@

\subsection{Description of experiments}

>>>>

\cmtDK[inline]{15 pages}
\cmtDK[inline]{\\
    - what is ambiguity? \\
    - unambigous dataset: \\
    ---- target group = non-target group \\
    ---- all attributes shared, except for the color \\
    ---- \ \  --> describable with one 'word'
}
In this section I will describe which experiments were conducted to answer the \cmtDK{?}{questions} from the previous sections as well as the setup of these experiments. This will be done in two parts. The first part contains the creation of the datasets that will be used in the experiments. In the second part I will go deeper into discussing each experiment, including the necessity of the experiment, the specifities of the dataset, as well as the final architecture of the models.

@@

\subsection{Description of experiments}
Language games are very complex setups for machine learning models. The models need to solve multiple tasks at the same time to solve the overall problem. For instance in a simple setup of a game two agents are involved. The first agent, the sender is shown a scene with objects and needs to communicate on target object to the other agent, the receiver. The receiver is shown the same scene and needs to identify the target object with respect to the message of the sender. In this case, the sender first needs to learn to encode the scene as well as the information about the target object into its own \cmtDK{?}{space}. In a next step it needs to learn how to translate this encoding into a message that is sent to the receiver. The receiver then needs to learn to decode this message, after which it needs to learn how to combine the decoded message with its own encoding of the scene. And finally it needs to learn how to identify the target object with this information.

For this reason I decided to divide the main problem and let the models learn simpler subtasks and increase the complexity step by step. This will give me a very detailed overview, where the models struggle to learn and in which ways they can be improved. Mainly, I separated the tasks into language games with two agents (final experiments) and classical machine learning tasks without any communication, namely only one 'agent' that solves the task alone (pre-experiments). With this division, I can analyze the learning of the encodings of the scenes separately from the learning of producing and decoding messages.

\subsubsection{Pre-experiments without language games}
\paragraph{coordinate predictor}
\cmtDK[inline]{\\
    - pretrained ResNet/VGG\\
    - scratch \\
    - encoding of attributes (one-hot) \\
    - encoding of attributes (dale) \\
    - encoding of locations \\
    - masking}
\paragraph{bounding box classifier}

\paragraph{caption generator}
\cmtDK[inline]{\\
    - dale \\
    - masked}
\subsubsection{Language games}
